Distributed Range-Only Localisation that Preserves Sensor and Navigator Privacies

### 2021-06-03 main.tex
Missed mistake and some grammarly fixes

% Note that keywords are not normally used for peerreview papers.
\begin{IEEEkeywords}
State Estimation, Data Privacy, Sensor Fusion, Extended Kalman Filter.
\end{IEEEkeywords}

% For peerreview papers, this IEEEtran command inserts a page break and
% creates the second title. It will be ignored for other modes.
\IEEEpeerreviewmaketitle

@@

\subsection{Estimation problem} \label{subsec:est_problem}
The estimation problem we consider, for which we will reduce communication to the protocol above, is localisation with range-only sensors. In this work, we will focus on the two-dimensional case for simplicity but will derive methods suitable for extension to a three-dimensional equivalent. The state that we wish to estimate captures the navigator position and the change in position ($\Delta$), and is given by
\begin{equation}
    \vec{x} = 
    \begin{bmatrix}
        x & \Delta x & y & \Delta y
    \end{bmatrix}^\top\,. \label{eqn:state_definition}
\end{equation}
The state evolves following a known system model, which at timestep $k$ is given by
\begin{equation}
    \vec{x}_k = \vec{f}_k(\vec{x}_{k-1})+\vec{w}_k\,, \label{eqn:system_model}
\end{equation}
with system noise covariance $\mathsf{Cov}[\vec{w}_k]=\mat{Q}_k$. Measurements of the system follow a measurement model dependent on sensor $i$, $0\leq i \leq n$, given by 
\begin{equation}
    z_{k,i} = h_i(\vec{x}_k)+v_{k,i}\,, \label{eqn:measurement_model}
\end{equation}
with Gaussian measurement noises $v_{k,i} \sim \mathcal{N}(0,r_{k,i})$ and measurement function
\begin{equation}
    \begin{split}
        h_i(\vec{x}) &= \left\lVert
        \begin{bmatrix}
            x & y
        \end{bmatrix}^\top
        - \vec{s}_{i}\right\rVert \\
        &= \sqrt{(x-s_{x,i})^2 + (y-s_{y,i})^2}\,,
    \end{split}
\end{equation}
where
\begin{equation}
    \vec{s}_i = 
    \begin{bmatrix}
        s_{x,i} & s_{y,i}
    \end{bmatrix}^\top
\end{equation} 
is the location of sensor $i$.

@@

\section{Preliminaries} \label{sec:preliminaries}
When proposing an encryption scheme meeting the LCAO notion, we will base our method on the additively homomorphic Paillier encryption scheme \cite{paillierPublicKeyCryptosystemsBased1999} and the Joye-Libert privacy-preserving aggregation scheme \cite{joyeScalableSchemePrivacyPreserving2013}. These schemes have been summarised below. Additionally, the estimation problem we consider uses real-valued inputs and functions, and will require encoding real numbers for use with the aforementioned encryption schemes. The method used for encoding has been summarised afterwards.

@@

\begin{definition}
    An encryption scheme meets LCAO security if no adversary, running in probabilistic-time with respect to security parameter $\kappa$, has more than a negligible advantage in winning the above security game. Probabilities are taken over randomness introduced by $\mathcal{A}$, and in $\mathsf{Setup}$, $\mathsf{Enc}$ and $\mathsf{CombEnc}$.
\end{definition}

>>>>

% Key words
\begin{IEEEkeywords}
State Estimation, Data Privacy, Sensor Fusion, Extended Kalman Filter.
\end{IEEEkeywords}

% Creates the second title
\IEEEpeerreviewmaketitle

@@

\subsection{Estimation problem} \label{subsec:est_problem}
The estimation problem we consider, for which we will reduce communication to the protocol above, is localisation with range-only sensors. In this work, we will focus on the two-dimensional case for simplicity but will derive methods suitable for extension to a three-dimensional equivalent. The state that we wish to estimate captures the navigator position, and the change in position ($\Delta$), and is given by
\begin{equation}
    \vec{x} = 
    \begin{bmatrix}
        x & \Delta x & y & \Delta y
    \end{bmatrix}^\top\,. \label{eqn:state_definition}
\end{equation}
The state evolves following a known system model, which at timestep $k$ is given by
\begin{equation}
    \vec{x}_k = \vec{f}_k(\vec{x}_{k-1})+\vec{w}_k\,, \label{eqn:system_model}
\end{equation}
with system noise covariance $\mathsf{Cov}[\vec{w}_k]=\mat{Q}_k$. Measurements of the system follow a measurement model dependent on sensor $i$, $0\leq i \leq n$, given by 
\begin{equation}
    z_{k,i} = h_i(\vec{x}_k)+v_{k,i}\,, \label{eqn:measurement_model}
\end{equation}
with Gaussian measurement noises $v_{k,i} \sim \mathcal{N}(0,r_{k,i})$ and measurement function
\begin{equation}
    \begin{split}
        h_i(\vec{x}) &= \left\lVert
        \begin{bmatrix}
            x & y
        \end{bmatrix}^\top
        - \vec{s}_{i}\right\rVert \\
        &= \sqrt{(x-s_{x,i})^2 + (y-s_{y,i})^2}\,,
    \end{split}
\end{equation}
where
\begin{equation}
    \vec{s}_i = 
    \begin{bmatrix}
        s_{x,i} & s_{y,i}
    \end{bmatrix}^\top
\end{equation} 
is the location of sensor $i$.

@@

\section{Preliminaries} \label{sec:preliminaries}
When proposing an encryption scheme meeting the LCAO notion, we will base our method on the additively homomorphic Paillier encryption scheme \cite{paillierPublicKeyCryptosystemsBased1999} and the Joye-Libert privacy-preserving aggregation scheme \cite{joyeScalableSchemePrivacyPreserving2013}. These schemes have been summarised below. Additionally, the estimation problem we consider uses real-valued inputs and functions and will require encoding real numbers for use with the aforementioned encryption schemes. The method used for encoding has been summarised afterwards.

@@

\begin{definition}
    An encryption scheme meets LCAO security if no probabilistic adversary, running in polynomial-time with respect to security parameter $\kappa$, has more than a negligible advantage in winning the above security game. Probabilities are taken over randomness introduced by $\mathcal{A}$, and in $\mathsf{Setup}$, $\mathsf{Enc}$ and $\mathsf{CombEnc}$.
\end{definition}
